---
title: 'Comparing Ghani data with ours'
output:
  html_notebook: 
    number_sections: yes
  html_document: default
date: '`r Sys.Date()`'
---

```{r, echo = F, message = F, warning=FALSE, results='hide'}
rm(list = ls())
library(tidyverse); library(haven); library(ggthemes); library(stringr)

## Load the data
load("../data/1 Cleaned files for analysis/districtCorrespondence.RDA")
load("../data/1 Cleaned files for analysis/spatialAll.RDA")
load("../data/1 Cleaned files for analysis/asiData.RDA")
load("../data/1 Cleaned files for analysis/districtDistances.RDA")
load("../data/1 Cleaned files for analysis/misAllocation.RDA")

outcomeVariables <- read_csv("../data/1 Cleaned files for analysis/asiOutcomes.csv")
controlVars <- read_csv("../data/1 Cleaned files for analysis/controlVariables.csv")

spatialData <- spatialAll %>% 
        arrange(id, spatial_data_yr, geography) %>% #imp. for later steps that used indexes
        group_by(id, spatial_data_yr) %>% #three obs. in the order rural, total, urban (since geo is sorted)
        mutate(urbanPopShare = pop[3]/pop[2]) %>% # urban/total
        ungroup()

##Keeping only the variables that we need
spatialData <- spatialData %>% 
        dplyr::select(one_of(c("id", "L1_name", "L2_name","geography", "spatial_data_yr", controlVars$varNames))) %>% 
        filter(geography == "Total")

## Removing islands and India/China districts
spatialData <- spatialData %>% 
        filter(!str_detect(L1_name, "India/China|Andaman & Nicobar|Lakshadweep"))

##Filtering districts that are not in the misallocation dataset
spatialData <- left_join(spatialData, districtCorrespondence, by = c("id" = "spatialId")) %>% ## join in the final id from the correspondence dataset
        filter(finalId %in% c(misAllocation$finalId, "3_7_95_0", "3_7_93_0", "3_7_94_0", "3_7_91_0", "3_7_92_0", "3_7_90_0", "3_7_98_0", "3_7_97_0", "3_7_96_0"))

##Filtering out the states in the ghani paper that were taken out
spatialData <- spatialData %>% 
        filter(!(L1_name %in% c("Dadra & Nagar Haveli", "Daman & Diu", "Jammu and Kashmir", "Tripura", "Manipur", "Nagaland", "Meghalaya", "Mizoram", "Assam")))

#4 Summarise the spatial data to the final id based on asi correspondence
spatialData <- spatialData %>% 
        group_by(finalId, spatial_data_yr, L1_name) %>% ## L1_name is a irrelavant grouping var since final id is more disaggregated. But i keep it for future use in the regressions
        summarise_if(is.numeric, mean) %>%  #checked for na values and there are none
        ungroup()

##Create the ASI variables
asiData <- asiData %>% 
        group_by(finalId, year) %>% ##summarising by the final id var
        summarise(nFactories = sum(mult * x1, na.rm = T), totPersonsEngaged = sum(mult * x8, na.rm = T), totValOutput = sum(mult * x19, na.rm = T)) %>% 
        mutate(year = ifelse(year == 2010, 2011, year)) %>%  # to match the year on the spatial dataset
        ungroup()

## join the asi data to the spatial dataset
spatialData <- left_join(spatialData, asiData, by = c("finalId", "spatial_data_yr" = "year"))

winsorize <- function(x){
        lim <- quantile(x, probs = c(0.01, 0.99), na.rm = T) ##calc. the bound [1%, 99%]
        x[ x < lim[1] ] <- lim[1] #replace with lower bound if below bound
        x[ x > lim[2] ] <- lim[2] #replace with upper bound if above bound
        x
}

spatialData <- spatialData %>% 
        group_by(finalId) %>% 
        filter(min(nFactories, na.rm = T) != 0) %>% 
        filter(min(totPersonsEngaged, na.rm = T) != 0) %>% 
        filter(min(totValOutput, na.rm = T) != 0) %>% 
        ungroup() %>% 
        mutate_at(outcomeVariables$varNames, winsorize) # winsorize all outcome variables
logFunction <- function(x) {
        log(x[2]) - log(x[1]) #each distr only has two values 2011 and 2001
}
nonLog <- function(x){
        x[2] - x[1]
}

spatialDataOutcomes <- spatialData[,1] #create an empty dataframe for joining y vars

for(i in 1:length(outcomeVariables$varNames)){ #loop through outcomes
        varName <- outcomeVariables$varNames[i] #pull outcome var name
        
        if(outcomeVariables$logs[i] == 1){ # check if its logs or regular
                tempColumn <- spatialData %>% 
                        group_by(finalId) %>% #nObs 2 = 2001, 2011
                        mutate_at(varName, logFunction) %>% #use logs
                        ungroup() %>% 
                        dplyr::select(one_of(varName))
                names(tempColumn) <- paste(varName, "LogDiff", sep = "")
        } else{
                finalVarName <- paste(varName, "Diff", sep = "")
                tempColumn <- spatialData %>% 
                        group_by(finalId) %>% 
                        mutate_at(varName, nonLog) %>% #use non logs
                        ungroup() %>% 
                        dplyr::select(one_of(varName))
                names(tempColumn) <- paste(varName, "Diff", sep = "")
        }
        spatialDataOutcomes <- cbind(spatialDataOutcomes, tempColumn) #join together
}

spatialDataOutcomes <- dplyr::select(spatialDataOutcomes, -finalId) #remove the id column

spatialData <- cbind(spatialData, spatialDataOutcomes)
yVarNames <- names(spatialDataOutcomes) # for use in the regression loop

rm("spatialDataOutcomes")

# spatialData <- spatialData %>% 
#         filter(spatial_data_yr == 2001) #keep only 2001 year (since we finshed calc for diff between 2001 and 2011)
districtDistances <- districtDistances %>% 
        mutate(id = as.character(id), state = as.character(state), district = as.character(district))

districtDistances <- left_join(districtCorrespondence, districtDistances, by = c("spatialId" = "id")) %>% 
        group_by(finalId) %>% ##summarising by the final id vars mapped to 2001
        summarise(state = state[1], district = district[1], gqDistance = mean(gqDistance), nsewDistance = mean(nsewDistance), gqStraightDistance = mean(gqStraightDistance), nsewStraightDistance = mean(nsewStraightDistance))

gqNodalDistrictFinalIds <- c("3_7_95_0", "3_7_93_0", "3_7_94_0", "3_7_91_0", "3_7_92_0", "3_7_90_0", "3_7_98_0", "3_7_97_0", "3_7_96_0", "3_27_519_0", "3_27_518_0", "3_9_142_0", "3_6_86_0", "3_6_88_0", "3_27_517_0", "3_19_342_0", "3_33_603_0", "3_9_140_0")

nsewNodalDistrictFinalIds <- c("3_7_95_0", "3_7_93_0", "3_7_94_0", "3_7_91_0", "3_7_92_0", "3_7_90_0", "3_7_98_0", "3_7_97_0", "3_7_96_0", "3_4_55_0", "3_9_142_0", "3_6_86_0", "3_6_88_0", "3_9_140_0", "3_28_536_0", "3_29_572_0", "3_32_595_0", "3_33_629_0", "3_9_164_0", "3_9_157_0")

districtDistances <- districtDistances %>% 
        mutate(gqDistType = ifelse(finalId %in% gqNodalDistrictFinalIds, "nodal", ifelse(gqDistance > 0 & gqDistance <= 40, "0-40", ifelse(gqDistance > 40 & gqDistance <= 100, "40-100", "> 100")))) %>% 
        mutate(nsewDistType = ifelse(finalId %in% nsewNodalDistrictFinalIds, "nodal", ifelse(nsewDistance > 0 & nsewDistance <= 40, "0-40", ifelse(nsewDistance > 40 & nsewDistance <= 100, "40-100", "> 100")))) %>% 
        dplyr::select(finalId, gqDistType, nsewDistType)

spatialData <- left_join(spatialData, districtDistances, by = "finalId")

rm(list = setdiff(ls(), c("spatialData", "districtCorrespondence", "misAllocation")))

# ghaniData <- read_dta("../data/Aarti Data/03. Final district level datasets/130730-arti-data-working_3.dta") %>% 
#         select(state_CONSISTENT, districtname, contains("plant"), contains("empt"), contains("output")) %>% 
#         write_csv(., "../data/Aarti Data/preCorrespondence.csv")


misAllocation <- misAllocation %>% 
        filter(year == 2000) %>% 
        select(state, district, finalId)

ghaniData <- read_csv("../data/Aarti Data/postCorrespondence.csv") %>% 
        mutate_at(3:22, as.numeric) %>% 
        gather(variable, value, 3:22) %>% 
        separate(variable, into = c("variable", "year"), "(?<=[a-z]) ?(?=[0-9])") %>% 
        spread(variable, value) %>% 
        mutate(year = as.integer(year)) %>% 
        select(-plant_size) %>% 
        left_join(., misAllocation, by = c("state_CONSISTENT" = "state", "districtname" = "district")) %>% 
        select(7, 3, 6, 4, 5) %>% 
        group_by(finalId, year) %>% 
        mutate_if(is.numeric, mean) %>% 
        ungroup()

spatialASIData <- spatialData %>%
        select(1:2, 12:14)
names(spatialASIData) <- names(ghaniData)

spatialDistance <- spatialData %>% 
        filter(spatial_data_yr == 2001) %>% 
        select(1, 18:19)

 allData <- rbind(ghaniData, spatialASIData) %>% 
         arrange(finalId, year) %>% 
         left_join(., spatialDistance, by = "finalId") %>% 
         left_join(., districtCorrespondence, by = "finalId") %>% 
         select(1, 9:10, 6:7, 2, 3:5)
 
 
rm(list = setdiff(ls(), ("allData")))
```
##Data steps
The data from Ghani et. al (2015) was converted into a long format panel dataset that now contains the years 2001 and 2011 for the variables on number of factories, employees and output.

The variables were added 

## Seeing trends across years
First I plot the mean values of the variables across the years.
```{r}
allData %>% 
        group_by(year) %>% 
        summarise_at(7:9, mean) %>% 
        gather(variable, value, 2:4) %>%
        mutate(variable = toupper(variable)) %>% 
        ggplot(aes(x = year, y = value)) +
        geom_line() +
        geom_point(colour = "blue", size = 2, alpha = 0.5) +
        geom_vline(xintercept = c(2001, 2011), colour = "red", size = 0.2, alpha = 0.8) +
        facet_wrap(~ variable, ncol = 1, scales = "free_y") +
        scale_x_continuous(breaks = c(1994, 2000, 2001, 2005, 2007, 2009, 2011)) +
        labs(y = "Variable Value (in respective units)", x = "Year") +
        theme_tufte() +
        theme(strip.text = element_text(size = 14), axis.title = element_text(size = 12), panel.grid.major.x = element_line(colour="darkgrey", size=0.1), panel.grid.major.y = element_line(colour="darkgrey", size=0.1))
```

There seems to be a kink in the 2001 data that we have, which probable is driving the results that we are seeing. Also, the value of output seems to have a spike in 2011 (along with 2001) in our data, not sure why that is. I wonder if they are using the same variable as we are. Theirs, seems pretty flat in comparison.

###Plots by the distance
The first plot shows the mean of the different variable across the distance categories for GQ.
```{r, fig.width=14}
allData %>% 
        filter(!is.na(gqDistType)) %>% 
        group_by(gqDistType, year) %>% 
        summarise_at(7:9, mean) %>% 
        gather(variable, value, 3:5) %>% 
        mutate(variable = toupper(variable)) %>% 
        ggplot(aes(x = year, y = value)) +
        geom_line() +
        geom_point(colour = "blue", size = 2, alpha = 0.5) +
        geom_vline(xintercept = c(2001, 2011), colour = "red", size = 0.2, alpha = 0.8, linetype = 1) +
        facet_grid(variable ~ gqDistType, scales = "free_y") +
        scale_x_continuous(breaks = c(1994, 2000, 2001, 2005, 2007, 2009, 2011)) +
        labs(y = "Variable Value (in respective units)", x = "Year") +
        theme_tufte() +
        theme(strip.text = element_text(size = 18), axis.title = element_text(size = 12), panel.grid.major.x = element_line(colour="darkgrey", size=0.1), panel.grid.major.y = element_line(colour="darkgrey", size=0.1))


```

The next chart is the same as the above, but for NSEW.
```{r, fig.width=14}
allData %>% 
        filter(!is.na(nsewDistType)) %>% 
        group_by(nsewDistType, year) %>% 
        summarise_at(7:9, mean) %>% 
        gather(variable, value, 3:5) %>% 
        mutate(variable = toupper(variable)) %>% 
        ggplot(aes(x = year, y = value)) +
        geom_line() +
        geom_point(colour = "blue", size = 2, alpha = 0.5) +
        geom_vline(xintercept = c(2001, 2011), colour = "red", size = 0.2, alpha = 0.8, linetype = 1) +
        facet_grid(variable ~ nsewDistType, scales = "free_y") +
        scale_x_continuous(breaks = c(1994, 2000, 2001, 2005, 2007, 2009, 2011)) +
        labs(y = "Variable Value (in respective units)", x = "Year") +
        theme_tufte() +
        theme(strip.text = element_text(size = 18), axis.title = element_text(size = 12), panel.grid.major.x = element_line(colour="darkgrey", size=0.1), panel.grid.major.y = element_line(colour="darkgrey", size=0.1))
```


It seems that the data that we have is inflating the values for both 2001 and 2011 for output, while for the rest of the variables there seems to be kinks around 2001. Employment in nodal cities weirdly drop a bit in nodal districts while the other two variables seem to be higher than the trend.
