---
title: 'Regression with different years'
output:
  html_notebook: 
    number_sections: yes
  html_document: default
date: '`r Sys.Date()`'
---
##Data preprocessing steps
The same data processing steps as before (combination of our data cleaning along with steps in Ghani) are followed for the ASI 2001 and 2011 data. This data is then merged with the Ghani data.


```{r, echo = F, message = F, warning=FALSE, results='hide'}
rm(list = ls())
library(tidyverse); library(haven); library(ggthemes); library(stringr); library(sandwich); library(lmtest); library(stargazer); library(broom)

## Load the data
load("../data/1 Cleaned files for analysis/districtCorrespondence.RDA")
load("../data/1 Cleaned files for analysis/spatialAll.RDA")
load("../data/1 Cleaned files for analysis/asiData.RDA")
load("../data/1 Cleaned files for analysis/districtDistances.RDA")
load("../data/1 Cleaned files for analysis/misAllocation.RDA")

outcomeVariables <- read_csv("../data/1 Cleaned files for analysis/asiOutcomes.csv")
controlVars <- read_csv("../data/1 Cleaned files for analysis/controlVariables.csv")

## Create the urbanization variable
spatialData <- spatialAll %>% 
        arrange(id, spatial_data_yr, geography) %>% #imp. for later steps that used indexes
        group_by(id, spatial_data_yr) %>% #three obs. in the order rural, total, urban (since geo is sorted)
        mutate(urbanPopShare = pop[3]/pop[2]) %>% # urban/total
        ungroup()

##Keeping only the variables that we need
spatialData <- spatialData %>% 
        dplyr::select(one_of(c("id", "L1_name", "L2_name","geography", "spatial_data_yr", controlVars$varNames))) %>% 
        filter(geography == "Total")

## Removing islands and India/China districts
spatialData <- spatialData %>% 
        filter(!str_detect(L1_name, "India/China|Andaman & Nicobar|Lakshadweep"))

##Filtering districts that are not in the misallocation dataset
spatialData <- left_join(spatialData, districtCorrespondence, by = c("id" = "spatialId")) %>% ## join in the final id from the correspondence dataset
        filter(finalId %in% c(misAllocation$finalId, "3_7_95_0", "3_7_93_0", "3_7_94_0", "3_7_91_0", "3_7_92_0", "3_7_90_0", "3_7_98_0", "3_7_97_0", "3_7_96_0"))

##Filtering out the states in the ghani paper that were taken out
spatialData <- spatialData %>% 
        filter(!(L1_name %in% c("Dadra & Nagar Haveli", "Daman & Diu", "Jammu and Kashmir", "Tripura", "Manipur", "Nagaland", "Meghalaya", "Mizoram", "Assam")))

#4 Summarise the spatial data to the final id based on asi correspondence
spatialData <- spatialData %>% 
        group_by(finalId, spatial_data_yr, L1_name) %>% ## L1_name is a irrelavant grouping var since final id is more disaggregated. But i keep it for future use in the regressions
        summarise_if(is.numeric, mean) %>%  #checked for na values and there are none
        ungroup()

##Create the ASI variables
asiData <- asiData %>% 
        group_by(finalId, year) %>% ##summarising by the final id var
        summarise(nFactories = sum(mult * x1, na.rm = T), totPersonsEngaged = sum(mult * x8, na.rm = T), totValOutput = sum(mult * x19, na.rm = T)) %>% 
        mutate(year = ifelse(year == 2010, 2011, year)) %>%  # to match the year on the spatial dataset
        ungroup()

## join the asi data to the spatial dataset
spatialData <- left_join(spatialData, asiData, by = c("finalId", "spatial_data_yr" = "year"))


##Adding the district distances
districtDistances <- districtDistances %>% 
        mutate(id = as.character(id), state = as.character(state), district = as.character(district))

districtDistances <- left_join(districtCorrespondence, districtDistances, by = c("spatialId" = "id")) %>% 
        group_by(finalId) %>% ##summarising by the final id vars mapped to 2001
        summarise(state = state[1], district = district[1], gqDistance = mean(gqDistance), nsewDistance = mean(nsewDistance), gqStraightDistance = mean(gqStraightDistance), nsewStraightDistance = mean(nsewStraightDistance))

gqNodalDistrictFinalIds <- c("3_7_95_0", "3_7_93_0", "3_7_94_0", "3_7_91_0", "3_7_92_0", "3_7_90_0", "3_7_98_0", "3_7_97_0", "3_7_96_0", "3_27_519_0", "3_27_518_0", "3_9_142_0", "3_6_86_0", "3_6_88_0", "3_27_517_0", "3_19_342_0", "3_33_603_0", "3_9_140_0")

nsewNodalDistrictFinalIds <- c("3_7_95_0", "3_7_93_0", "3_7_94_0", "3_7_91_0", "3_7_92_0", "3_7_90_0", "3_7_98_0", "3_7_97_0", "3_7_96_0", "3_4_55_0", "3_9_142_0", "3_6_86_0", "3_6_88_0", "3_9_140_0", "3_28_536_0", "3_29_572_0", "3_32_595_0", "3_33_629_0", "3_9_164_0", "3_9_157_0")

districtDistances <- districtDistances %>% 
        mutate(gqDistType = ifelse(finalId %in% gqNodalDistrictFinalIds, "nodal", ifelse(gqDistance > 0 & gqDistance <= 40, "0-40", ifelse(gqDistance > 40 & gqDistance <= 100, "40-100", "> 100")))) %>% 
        mutate(nsewDistType = ifelse(finalId %in% nsewNodalDistrictFinalIds, "nodal", ifelse(nsewDistance > 0 & nsewDistance <= 40, "0-40", ifelse(nsewDistance > 40 & nsewDistance <= 100, "40-100", "> 100")))) %>% 
        dplyr::select(finalId, gqDistType, nsewDistType)

spatialData <- left_join(spatialData, districtDistances, by = "finalId")


## Create the combined outcome variables
misAllocation <- misAllocation %>% 
        filter(year == 2000) %>% 
        select(state, district, finalId)
ghaniDistances <- read_dta("../data/Aarti Data/03. Final district level datasets/130930-arti-data-working.dta") %>% 
        select(contains("dis"))

ghaniData <- read_csv("../data/Aarti Data/postCorrespondence.csv") %>% 
        mutate_at(3:22, as.numeric) %>% 
        gather(variable, value, 3:22) %>% 
        separate(variable, into = c("variable", "year"), "(?<=[a-z]) ?(?=[0-9])") %>% 
        spread(variable, value) %>% 
        mutate(year = as.integer(year)) %>% 
        select(-plant_size) %>% 
        left_join(., misAllocation, by = c("state_CONSISTENT" = "state", "districtname" = "district")) %>% 
        select(7, 3, 6, 4, 5) %>% 
        group_by(finalId, year) %>% 
        mutate_if(is.numeric, mean) %>% 
        ungroup()

spatialASIData <- spatialData %>%
        select(1:2, 12:14)
names(ghaniData) <- names(spatialASIData)

spatialDistance <- spatialData %>% 
        filter(spatial_data_yr == 2001) %>% 
        select(1, 15:16)

 allData <- rbind(ghaniData, spatialASIData) %>% 
         arrange(finalId, spatial_data_yr) %>% 
         left_join(., spatialDistance, by = "finalId") %>% 
         left_join(., districtCorrespondence, by = "finalId") %>% 
         select(1, 9:10, 6:7, year = spatial_data_yr, 3:5)

 ## Create the control variables
 spatialControls <- spatialData %>% 
         filter(spatial_data_yr == 2001) %>% 
         select(finalId, L1_name, one_of(controlVars$varNames))
 
 allData <- left_join(allData, spatialControls, by = "finalId")
  
rm(list = setdiff(ls(), c("allData", "outcomeVariables", "controlVars")))
```

##Regressions
There are three specifications of interest

1. Start Year = 2001 to End Year = 2011
2. Start Year = 2000 to End Year = 2009/7
3. Start Year = 2000 to End Year = 2011

```{r}
##Winsorizing the outcome variables
winsorize <- function(x){
        lim <- quantile(x, probs = c(0.01, 0.99), na.rm = T) ##calc. the bound [1%, 99%]
        x[ x < lim[1] ] <- lim[1] #replace with lower bound if below bound
        x[ x > lim[2] ] <- lim[2] #replace with upper bound if above bound
        x
}


        
```

##Regression 1 Start Year 2001 and end Year 2011

```{r}

##Create the data (select the years of interest and winsorize the data)
regressionData <- allData %>% 
        filter(year == 2001 | year == 2011) %>%
        group_by(finalId) %>% 
        filter(min(nFactories, na.rm = T) != 0) %>% 
        filter(min(totPersonsEngaged, na.rm = T) != 0) %>% 
        filter(min(totValOutput, na.rm = T) != 0) %>% 
        ungroup() %>% 
        mutate_at(outcomeVariables$varNames, winsorize) # winsorize all outcome variables

##Calculate the outcome variables based on the start and end year
regressionData <- regressionData %>%
        group_by(finalId) %>% 
        arrange(finalId, year) %>% 
        mutate(nFactoriesLogDiff = log(nFactories[2]) - log(nFactories[1]), totPersonsEngagedLogDiff = log(totPersonsEngaged[2]) - log(totPersonsEngaged[1]), totValOutputLogDiff = log(totValOutput[2]) - log(totValOutput[1])) %>% 
        ungroup() %>% 
        filter(year == 2001)

for(i in 1:length(outcomeVariables$varNames)){
        yOutcomeName <- paste(outcomeVariables$varNames[i], "LogDiff", sep = "")
        yOutcomeValues <- regressionData %>% 
                select(one_of(yOutcomeName)) %>%
                unlist(use.names = FALSE)
        yControlValues <- regressionData %>% 
                select(one_of(outcomeVariables$varNames[i])) %>%
                unlist(use.names = FALSE)
        gqDistance <- regressionData %>% 
                mutate(gqDistType = factor(gqDistType, levels = c("> 100", "nodal", "0-40", "40-100"))) %>% 
                select(gqDistType) %>% 
                unlist(use.names = FALSE)
        
        nsewDistance <- regressionData %>% 
                mutate(nsewDistType = factor(nsewDistType, levels = c("> 100", "nodal", "0-40", "40-100"))) %>%
                select(nsewDistType) %>% 
                unlist(use.names = FALSE)
        
        stateControls <- regressionData %>% 
                select(state = L1_name) %>% 
                unlist(use.names = FALSE)
        
        #3. Create variables for the tables
        depVarLabel <- outcomeVariables[i,]$varDescription
        title <- outcomeVariables$title[i]
        outString <- paste("../Results/Tables/ASI Regressions Mar 9th/", title, " ", "2001", "-", "2011", ".html", sep = "")
        
        #4. Specify the models
        model0 <- lm(yOutcomeValues ~ gqDistance + nsewDistance)
        cov0 <- vcovHC(model0, type = "HC1")
        robust_se0 <- sqrt(diag(cov0))

        model1 <- lm(yOutcomeValues ~ gqDistance + nsewDistance + yControlValues)
        cov1 <- vcovHC(model1, type = "HC1")
        robust_se1 <- sqrt(diag(cov1))

        model2 <- lm(yOutcomeValues ~ gqDistance + nsewDistance + yControlValues + as.factor(stateControls))
        cov2 <- vcovHC(model2, type = "HC1")
        robust_se2 <- sqrt(diag(cov2))

        model3 <- lm(yOutcomeValues ~ gqDistance)
        cov3 <- vcovHC(model3, type = "HC1")
        robust_se3 <- sqrt(diag(cov3))

        model4 <- lm(yOutcomeValues ~ gqDistance + yControlValues)
        cov4 <- vcovHC(model4, type = "HC1")
        robust_se4 <- sqrt(diag(cov4))

        model5 <- lm(yOutcomeValues ~ gqDistance + yControlValues + as.factor(stateControls))
        cov5 <- vcovHC(model5, type = "HC1")
        robust_se5 <- sqrt(diag(cov5))

        stargazer(model0, model1, model2, model3, model4, model5, se = list(robust_se0, robust_se1, robust_se2, robust_se3, robust_se4, robust_se5),  dep.var.labels = depVarLabel, omit = "L1", type = "html", out = outString)
}        
```

##Regression 2 Start Year 2000 and end Year 2009/7

```{r}


##Create the data (select the years of interest and winsorize the data)
regressionData <- allData %>% 
        filter(year %in% c(2000, 2007, 2009)) %>%
        group_by(finalId) %>% 
        filter(min(nFactories, na.rm = T) != 0) %>% 
        filter(min(totPersonsEngaged, na.rm = T) != 0) %>% 
        filter(min(totValOutput, na.rm = T) != 0) %>% 
        ungroup() %>% 
        mutate_at(outcomeVariables$varNames, winsorize) # winsorize all outcome variables

##Calculate the outcome variables based on the start and end year
regressionData <- regressionData %>%
        group_by(finalId) %>% 
        arrange(finalId, year) %>% 
        mutate(nFactoriesLogDiff = log((nFactories[3] + nFactories[2])/(2 * nFactories[1])), totPersonsEngagedLogDiff = log((totPersonsEngaged[3] + totPersonsEngaged[2])/(2 * totPersonsEngaged[1])), totValOutputLogDiff = log((totValOutput[3] + totValOutput[2])/(2 * totValOutput[1]))) %>% 
        ungroup() %>% 
        filter(year == 2000)

for(i in 1:length(outcomeVariables$varNames)){
        yOutcomeName <- paste(outcomeVariables$varNames[i], "LogDiff", sep = "")
        yOutcomeValues <- regressionData %>% 
                select(one_of(yOutcomeName)) %>%
                unlist(use.names = FALSE)
        yControlValues <- regressionData %>% 
                select(one_of(outcomeVariables$varNames[i])) %>%
                unlist(use.names = FALSE)
        gqDistance <- regressionData %>% 
                mutate(gqDistType = factor(gqDistType, levels = c("> 100", "nodal", "0-40", "40-100"))) %>% 
                select(gqDistType) %>% 
                unlist(use.names = FALSE)
        
        nsewDistance <- regressionData %>% 
                mutate(nsewDistType = factor(nsewDistType, levels = c("> 100", "nodal", "0-40", "40-100"))) %>%
                select(nsewDistType) %>% 
                unlist(use.names = FALSE)
        
        stateControls <- regressionData %>% 
                select(state = L1_name) %>% 
                unlist(use.names = FALSE)
        
        popWeights <- regressionData %>% 
                mutate(lnPop = log(pop)) %>% 
                select(lnPop) %>% 
                unlist(use.names = FALSE)
        
        #3. Create variables for the tables
        depVarLabel <- outcomeVariables[i,]$varDescription
        title <- outcomeVariables$title[i]
        outString <- paste("../Results/Tables/ASI Regressions Mar 9th/", title, " ", "2000", "-", "2009", ".html", sep = "")
        
        #4. Specify the models
        model0 <- lm(yOutcomeValues ~ gqDistance + nsewDistance, weights = popWeights)
        cov0 <- vcovHC(model0, type = "HC1")
        robust_se0 <- sqrt(diag(cov0))

        model1 <- lm(yOutcomeValues ~ gqDistance + nsewDistance + yControlValues, weights = popWeights)
        cov1 <- vcovHC(model1, type = "HC1")
        robust_se1 <- sqrt(diag(cov1))

        model2 <- lm(yOutcomeValues ~ gqDistance + nsewDistance + yControlValues + as.factor(stateControls), weights = popWeights)
        cov2 <- vcovHC(model2, type = "HC1")
        robust_se2 <- sqrt(diag(cov2))

        model3 <- lm(yOutcomeValues ~ gqDistance, weights = popWeights)
        cov3 <- vcovHC(model3, type = "HC1")
        robust_se3 <- sqrt(diag(cov3))

        model4 <- lm(yOutcomeValues ~ gqDistance + yControlValues, weights = popWeights)
        cov4 <- vcovHC(model4, type = "HC1")
        robust_se4 <- sqrt(diag(cov4))

        model5 <- lm(yOutcomeValues ~ gqDistance + yControlValues + as.factor(stateControls), weights = popWeights)
        cov5 <- vcovHC(model5, type = "HC1")
        robust_se5 <- sqrt(diag(cov5))

        stargazer(model0, model1, model2, model3, model4, model5, se = list(robust_se0, robust_se1, robust_se2, robust_se3, robust_se4, robust_se5),  dep.var.labels = depVarLabel, omit = "L1", type = "html", out = outString)
}        
```

##Regression with Start Year 2000 and End Year 2011

```{r}

##Create the data (select the years of interest and winsorize the data)
regressionData <- allData %>% 
        filter(year == 2000 | year == 2011) %>%
        group_by(finalId) %>% 
        filter(min(nFactories, na.rm = T) != 0) %>% 
        filter(min(totPersonsEngaged, na.rm = T) != 0) %>% 
        filter(min(totValOutput, na.rm = T) != 0) %>% 
        ungroup() %>% 
        mutate_at(outcomeVariables$varNames, winsorize) # winsorize all outcome variables

##Calculate the outcome variables based on the start and end year
regressionData <- regressionData %>%
        group_by(finalId) %>% 
        arrange(finalId, year) %>% 
        mutate(nFactoriesLogDiff = log(nFactories[2]) - log(nFactories[1]), totPersonsEngagedLogDiff = log(totPersonsEngaged[2]) - log(totPersonsEngaged[1]), totValOutputLogDiff = log(totValOutput[2]) - log(totValOutput[1])) %>% 
        ungroup() %>% 
        filter(year == 2000)

for(i in 1:length(outcomeVariables$varNames)){
        yOutcomeName <- paste(outcomeVariables$varNames[i], "LogDiff", sep = "")
        yOutcomeValues <- regressionData %>% 
                select(one_of(yOutcomeName)) %>%
                unlist(use.names = FALSE)
        yControlValues <- regressionData %>% 
                select(one_of(outcomeVariables$varNames[i])) %>%
                unlist(use.names = FALSE)
        gqDistance <- regressionData %>% 
                mutate(gqDistType = factor(gqDistType, levels = c("> 100", "nodal", "0-40", "40-100"))) %>% 
                select(gqDistType) %>% 
                unlist(use.names = FALSE)
        
        nsewDistance <- regressionData %>% 
                mutate(nsewDistType = factor(nsewDistType, levels = c("> 100", "nodal", "0-40", "40-100"))) %>%
                select(nsewDistType) %>% 
                unlist(use.names = FALSE)
        
        stateControls <- regressionData %>% 
                select(state = L1_name) %>% 
                unlist(use.names = FALSE)
        
        #3. Create variables for the tables
        depVarLabel <- outcomeVariables[i,]$varDescription
        title <- outcomeVariables$title[i]
        outString <- paste("../Results/Tables/ASI Regressions Mar 9th/", title, " ", "2000", "-", "2011", ".html", sep = "")
        
        #4. Specify the models
        model0 <- lm(yOutcomeValues ~ gqDistance + nsewDistance)
        cov0 <- vcovHC(model0, type = "HC1")
        robust_se0 <- sqrt(diag(cov0))

        model1 <- lm(yOutcomeValues ~ gqDistance + nsewDistance + yControlValues)
        cov1 <- vcovHC(model1, type = "HC1")
        robust_se1 <- sqrt(diag(cov1))

        model2 <- lm(yOutcomeValues ~ gqDistance + nsewDistance + yControlValues + as.factor(stateControls))
        cov2 <- vcovHC(model2, type = "HC1")
        robust_se2 <- sqrt(diag(cov2))

        model3 <- lm(yOutcomeValues ~ gqDistance)
        cov3 <- vcovHC(model3, type = "HC1")
        robust_se3 <- sqrt(diag(cov3))

        model4 <- lm(yOutcomeValues ~ gqDistance + yControlValues)
        cov4 <- vcovHC(model4, type = "HC1")
        robust_se4 <- sqrt(diag(cov4))

        model5 <- lm(yOutcomeValues ~ gqDistance + yControlValues + as.factor(stateControls))
        cov5 <- vcovHC(model5, type = "HC1")
        robust_se5 <- sqrt(diag(cov5))

        stargazer(model0, model1, model2, model3, model4, model5, se = list(robust_se0, robust_se1, robust_se2, robust_se3, robust_se4, robust_se5),  dep.var.labels = depVarLabel, omit = "L1", type = "html", out = outString)
}  
```
