---
title: "Spatial Regressions with 1999 base year"
output:
  html_notebook:
    number_sections: yes
  html_document: default
  pdf_document: default
date: '`r Sys.Date()`'
---

##Summary
This file reruns the initial set of regressions. The changes to the data are as follows.
1. The base year is now 1999 instead of 2001
2. In the earlier version the variables had been summarised (to the 2001 level) using simple means. In this version, levels are summed, and averages/rates are averaged (using weights were appropriate).

##Setting the data up for regressions
```{r}
rm(list = ls())
library(tidyverse); library(haven); library(stringr); library(sandwich); library(lmtest); library(stargazer); library(broom)

load("../data/1 Cleaned files for analysis/allData.RDA")
```

The cleaned dataset contains variables and years that are not from the spatial dataset. So I select these out.

```{r, message=FALSE}
varsOfInterest <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/allVarsFinal.csv") %>% 
        filter(source == "spatial") %>% 
        filter(!duplicated(varNames)) %>%
        arrange(varNames)

allData <- allData %>% 
        filter(year == 2001 | year == 2011) %>% 
        select(finalId, year, one_of(varsOfInterest$varNames))
        
```

The next step I calculate the 2011 - 2001 for each variable (some are log(2011) - log(2011))
```{r}


```

