---
title: "Running Regressions: basic specifications"
output:
  html_notebook:
    number_sections: yes
  html_document: default
  pdf_document: default
date: '`r Sys.Date()`'
---

##Summary
This file runs basic specifications on the list of Y vars. I use the package 'plm' to run the panel regression. You can read more about the package [here](http://ftp.uni-bayreuth.de/math/statlib/R/CRAN/doc/vignettes/plm/plmEN.pdf).

##Loading the datasets
I identify the y variables that we are interested in (by removing urban/rural and sector splits)
```{r, message=FALSE}
rm(list = ls())
library(tidyverse); library(plm); library(broom); library(stringr)
##The regression data
load("../data/1 Cleaned files for analysis/allData.RDA")

##The list of variables
varsOfInterest <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/allVarsFinal.csv") %>% 
        filter(varType == "y" & source != "ASI" & !str_detect(varNames, "_rur|_urb|agrEmp|mfgEmp|comEmp|trspEmp")) %>%  ##the current data does not have the ASI variables.
        select(varNames, description)

```

##Getting the data ready
For this set of regressions we are only interested in the y, the treatment and post variables.

```{r}
allData <- allData %>% 
        select(finalId, year, spatialState, gqDistType, nsewDistType, postGQ, postNSEW, one_of(varsOfInterest$varNames)) 
```


##Running the regression

###The specifications
<span style="background-color:#FFD701">A few things to note:</span>

1. `*` indicates an interaction so `State * Year` is the interaction of states with the year variable.
2. Both the specification have district fixed effects and not year effects (this can be changed easily).
3. Also, not sure if I need to include the distance bands in the specification since they would be swallowed by the district fixed effects. Right?
4. I haven't done any sort of data transformations (logs etc) other than winsorizing all the outcome variables (in the file I sent out yesterday).

The current specifications are as follows, (I have included examples of the specification so that you can see the model characteristics):

**Spec 1:** $$Y_{i,t} = Distance^{GQ}_{i} + Distance^{GQ}_{i}*Post^{GQ}_{i,t} + Distance^{NSEW}_{i} + Distance^{NSEW}_{i}*Post^{NSEW}_{i,t} + District_{i}$$
```{r}
spec1 <- plm(povrate_tot ~ gqDistType + gqDistType * postGQ + nsewDistType + nsewDistType * postNSEW, data = allData)
summary(spec1)
rm("spec1")
```

**Spec 2:** 
$$Y_{i,t} = Distance^{GQ}_{i} + Distance^{GQ}_{i}*Post^{GQ}_{i,t} + Distance^{NSEW}_{i} + Distance^{NSEW}_{i}*Post^{NSEW}_{i,t} + District_{i} + State * Year$$

I haven't included a sample of the output here to save space since the list of coefficients is long with state * year

###Looping through y variables
The code below loops through all the y values to run the two specifications
```{r}
varList <- varsOfInterest$varNames
results1 <- lapply(allData[, varList], function(x) plm(x ~ gqDistType + gqDistType * postGQ + nsewDistType + nsewDistType * postNSEW, data = allData)) ##looping through all the y variables
results2 <- lapply(allData[, varList], function(x) plm(x ~ gqDistType + gqDistType * postGQ + nsewDistType + nsewDistType * postNSEW + spatialState * year, data = allData))
```

###Tidying the results to create a table
Specification 1
```{r}
tidyResults1 <- NULL
for(i in 1:length(varList)) {
        varDesc <- varsOfInterest[i, ]$description
        if(i == 1){
                tidyResults1 <- tidy(results1[[1]]) %>% 
                        mutate(variable = varDesc)
        } else {
                tempResults <- tidy(results1[[i]]) %>% 
                        mutate(variable = varDesc)
                tidyResults1 <- rbind(tidyResults1, tempResults)      
        }
}
commonTerms <- unique(tidyResults1$term)
tidyResults1 <- tidyResults1 %>% 
        mutate(estimate = ifelse(p.value <= 0.01, paste(round(estimate, 2), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 2), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 2), "*", sep=""), as.character(round(estimate, 2)))))) %>% 
        select(variable, 1, 2) %>% 
        spread(term, estimate)
        
names(tidyResults1) <- c("variable", "GQ(0-40) * Post", "GQ(40-100) * Post", "GQ(Nodal) * Post", "NSEW(0-40) * Post", "NSEW(40-100) * Post", "NSEW(Nodal) * Post", "Post(GQ)", "Post(NSEW)")
        # mutate_at(2:5, .funs = funs(round(., 2))) %>% 
        # select(variable, 1:5) %>%
        # mutate(significance = ifelse(p.value < 0.01, "***", ifelse(p.value < 0.05, "**", "")))

rm("results1")
```

Specification 2
```{r}
tidyResults2 <- NULL
for(i in 1:length(varList)) {
        varDesc <- varsOfInterest[i, ]$description
        if(i == 1){
                tidyResults2 <- tidy(results2[[1]]) %>% 
                        filter(term %in% unique(commonTerms)) %>% 
                        mutate(variable = varDesc)
        } else {
                tempResults <- tidy(results2[[i]]) %>% 
                        filter(term %in% unique(commonTerms)) %>% 
                        mutate(variable = varDesc)
                tidyResults2 <- rbind(tidyResults2, tempResults)        
        }
}
tidyResults2 <- tidyResults2 %>%
        mutate(estimate = ifelse(p.value <= 0.01, paste(round(estimate, 2), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 2), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 2), "*", sep=""), as.character(round(estimate, 2)))))) %>% 
        select(variable, 1, 2) %>% 
        spread(term, estimate)
        # mutate_at(2:5, .funs = funs(round(., 2))) %>% 
        # select(variable, 1:5) %>% 
        # mutate(significance = ifelse(p.value < 0.01, "***", ifelse(p.value < 0.05, "**", "")))
names(tidyResults2) <- c("variable", "GQ(0-40) * Post", "GQ(40-100) * Post", "GQ(Nodal) * Post", "NSEW(0-40) * Post", "NSEW(40-100) * Post", "NSEW(Nodal) * Post", "Post(GQ)", "Post(NSEW)")
rm(list = setdiff(ls(), c("tidyResults1", "tidyResults2")))
head(tidyResults2, n = 8)
```

Saving the 'tidied' results
```{r}
write_csv(tidyResults1, "../Results/Tables/spec1_Apr5.csv")
write_csv(tidyResults2, "../Results/Tables/spec2_Apr5.csv")
```

