---
title: "Running Regressions: Identifying the Z vars"
output:
  html_notebook:
    number_sections: yes
  html_document: default
  pdf_document: default
date: '`r Sys.Date()`'
---
##Summary and Methodology
This file iterates through all the combinations of the z variables to identify the best combination of z vars for each outcome of interest. The z vars themselves are categorize into 4 markets (capital, labour, land and product) and the final configuration for each outcome requires one z var for each of these categories.

Each regression has the same specification structure(only the z vars are changed):
$$Y_{i,t} = Distance^{GQ}_{i} + Distance^{NSEW}_{i} + Z^{capital}_{i,t} + Z^{labour}_{i,t} + Z^{land}_{i,t} + Z^{product}_{i,t} + Distance^{GQ}_{i}*Post^{GQ}_{i,t} + Distance^{NSEW}_{i}*Post^{NSEW}_{i,t} + \\Distance^{GQ}_{i}*Post^{GQ}_{i,t}*Z^{capital}_{i,t} + Distance^{GQ}_{i}*Post^{GQ}_{i,t}*Z^{labour}_{i,t} + Distance^{GQ}_{i}*Post^{GQ}_{i,t}*Z^{land}_{i,t} + Distance^{GQ}_{i}*Post^{GQ}_{i,t}*Z^{product}_{i,t} \\+ Distance^{NSEW}_{i}*Post^{NSEW}_{i,t}*Z^{capital}_{i,t} + Distance^{NSEW}_{i}*Post^{NSEW}_{i,t}*Z^{labour}_{i,t} + Distance^{NSEW}_{i}*Post^{NSEW}_{i,t}*Z^{land}_{i,t} +\\ Distance^{NSEW}_{i}*Post^{NSEW}_{i,t}*Z^{product}_{i,t} + State * Year$$


##Loading the datasets
```{r, message=FALSE, echo=FALSE}
rm(list = ls())
library(tidyverse); library(plm); library(broom); library(stringr)
##The regression data
load("../data/1 Cleaned files for analysis/allData.RDA")

##The list of variables
yVars <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/yVarsFinal.csv") %>% 
        select(varNames, yType, description) %>% 
        arrange(yType, varNames)

zVars <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/zVars.csv") %>% 
        arrange(zType, varNames)

```

##Getting the data ready
For this set of regressions we are only interested in the y, z, the treatment and post variables. <span style="background-color:#FFD701">The variable hous_slm only has data at the urban level and is therefore NA at the total geography level. So I remove this variable from our analysis.</span>
```{r}
allData <- allData %>% 
        select(finalId, year, spatialState, gqDistType, nsewDistType, postGQ, postNSEW, one_of(yVars$varNames, zVars$varNames))
```

Next I create the entire set of combinations (300 = 3 x 5 x 5 x 4) of z variables to be used for the regressions. Each Y variable will be iterated through these combinations.

```{r}
##Split the z variables based on their market categgories
capitalVars <- zVars %>% 
        filter(zType == "Capital market") %>% 
        select(varNames) %>% 
        unlist(use.names = F)
labourVars <- zVars %>% 
        filter(zType == "Labor market") %>% 
        select(varNames) %>% 
        unlist(use.names = F)
landVars <- zVars %>% 
        filter(zType == "Land market") %>% 
        select(varNames) %>% 
        unlist(use.names = F)
productVars <- zVars %>% 
        filter(zType == "Product market") %>% 
        select(varNames) %>% 
        unlist(use.names = F)

##Create a data frame with the different combinations
allCombinations <- expand.grid(capitalVar = capitalVars, labourVar = labourVars, landVar = landVars, productVar = productVars)

# model <- (plm(pct_selfemp_both_tot ~ gqDistType + nsewDistType + bank_t + edu_ter_15_t+ cr_s + e_own1 + gqDistType * postGQ + nsewDistType * postNSEW + gqDistType * postGQ * bank_t + gqDistType * postGQ * edu_ter_15_t + gqDistType * postGQ * cr_s + gqDistType * postGQ * e_own1 + nsewDistType * postNSEW * bank_t + nsewDistType * postNSEW * edu_ter_15_t + nsewDistType * postNSEW * cr_s + nsewDistType * postNSEW * e_own1 + gqDistType*postGQ*nsewDistType*postNSEW + spatialState * year, data = allData))




```


##Running the regressions
We are interested in the terms on the 8 z variable $Distance^{GQ/NSEW}_{i, 0-40}*Post^{GQ/NSEW}_{i,t}*Z^{J}_{i,t}$ (for both GQ and NSEW) and the two $Distance^{GQ/NSEW}_{i, 0-40}*Post^{GQ/NSEW}_{i,t}$ terms. In the code chunk below, I loop through all the 300 combinations of the four z variables (one from each product market) for each of the outcomes. I store these results as a data frame.

```{r}
pattern <- "(?=.*DistType0-40)(?=.*post)"
yLoop <- function(y){
        ##select the y variable
        depVar <- unlist(allData[y], use.names = F)
        
        regressionFunction <- function(x){ ##selects the variables and runs regression
                result <- list()
                ##Select all the z variables
                capitalVar <- unlist(allData[x[1]], use.names = F)
                labourVar <- unlist(allData[x[2]], use.names = F)
                landVar <- unlist(allData[x[3]], use.names = F)
                productVar <- unlist(allData[x[4]], use.names = F)
                zVarCombo <- paste(x[1], x[2], x[3], x[4], sep = ",")
                ##Regression
                model <- plm(depVar ~ gqDistType + nsewDistType + capitalVar + labourVar+ landVar + productVar + gqDistType * postGQ + nsewDistType * postNSEW + gqDistType * postGQ * capitalVar + gqDistType * postGQ * labourVar + gqDistType * postGQ * landVar + gqDistType * postGQ * productVar + nsewDistType * postNSEW * capitalVar + nsewDistType * postNSEW * labourVar + nsewDistType * postNSEW * landVar + nsewDistType * postNSEW * productVar + spatialState * year, data = allData)
                
                ##extracting model characteristics
                tidy(model) %>%
                        filter(str_detect(term, pattern)) %>%
                        mutate(zVarCombo = zVarCombo, yVar = y, adjRSq = glance(model)$adj.r.squared) %>%
                        select(yVar, zVarCombo, term, estimate, p.value, adjRSq)
        }
        
        ##loop through all the combinations and store the results
        apply(allCombinations, 1, regressionFunction)
}

yVarList <- yVars$varNames
resultsList <- lapply(yVarList, function(y) yLoop(y)) ## run the loop on the outcome variables

resultsListDF <- bind_rows(lapply(resultsList, bind_rows)) ##convert to data frame
        
write_csv(resultsListDF, "regressionResultsZVarsApr20NoQuad.csv") ##save
```







