---
title: "Regressions without Z variables"
output:
  html_notebook:
    number_sections: yes
  html_document: default
  pdf_document: default
date: '`r Sys.Date()`'
---
##Summary
This file runs different sets of regressions.

1. Base specification: With only GQ and NSEW terms and no z variables.
2. Market specification: With triple interaction terms with Z variables
3. Misallocation specification: With triple interaction terms with misallocation variables.
4. Base specification with continous distance instead of bands (as the treatement).

##Loading the datasets
```{r, message=FALSE}
rm(list = ls())
library(tidyverse); library(plm); library(broom); library(stringr); library(readxl)

##The regression data
load("../data/1 Cleaned files for analysis/allData.RDA")

resultsData <- read_excel("../Results/Tables/allResults.xlsx", sheet = 2) %>% 
        select(2, 5:8)

yVars <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/yVarsFinal.csv") %>% 
        select(varNames, yType, description) %>% 
        arrange(yType, varNames)

zVars <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/zVars.csv") %>% 
        arrange(zType, varNames)

zVarsMis <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/allVarsFinal.csv") %>% 
        select(varNames, zType, description) %>% 
        filter(varNames %in% c("mis_Y_3b", "mis_L_3b", "mis_T_3b", "mis_K_3b")) %>% 
        arrange(zType, varNames)

allDataMis <- allData %>%
        select(finalId, year, spatialState, gqDistType, nsewDistType, postGQ, postNSEW, one_of(zVarsMis$varNames, yVars$varNames))

```


##Running Regressions without Z vars using the same sample

The simplest specification include only the effects of the highways. It uses the following specification (no state year effects):
$$Y_{i,t} = Distance^{GQ}_{i} + Distance^{NSEW}_{i} + Distance^{GQ}_{i}*Post^{GQ}_{i,t} + Distance^{NSEW}_{i}*Post^{NSEW}_{i,t} + District_{i}$$

```{r}
regressionFunction <- function(x){
        depVar <- unlist(allData[x[1]], use.names = F)
        ##Select all the z variables
        capitalVar <- unlist(allData[x[2]], use.names = F)
        labourVar <- unlist(allData[x[3]], use.names = F)
        landVar <- unlist(allData[x[4]], use.names = F)
        productVar <- unlist(allData[x[5]], use.names = F)
        
        modelZ <- plm(depVar ~ gqDistType + nsewDistType + capitalVar + labourVar+ landVar + productVar + gqDistType * postGQ + nsewDistType * postNSEW + gqDistType * postGQ * capitalVar + gqDistType * postGQ * labourVar + gqDistType * postGQ * landVar + gqDistType * postGQ * productVar + nsewDistType * postNSEW * capitalVar + nsewDistType * postNSEW * labourVar + nsewDistType * postNSEW * landVar + nsewDistType * postNSEW * productVar + spatialState * year, data = allData)
        
        modelNames <- rownames(modelZ$model)
        sampleData <- allData[rownames(allData) %in% modelNames,]
        depVar <- unlist(sampleData[x[1]], use.names = F) ##update the y variable
        
        model <- plm(depVar ~ gqDistType + nsewDistType + gqDistType * postGQ + nsewDistType * postNSEW + spatialState * year, data = sampleData)
        
        tidy(model) %>% 
                filter(str_detect(term, "(?=.*DistType0-40)(?=.*post)|(^postGQ$)|(^postNSEW$)")) %>% 
                mutate(yVar = x[1], adjRSq = glance(model)$adj.r.squared) %>% 
                select(yVar, term, estimate, p.value, adjRSq)
}

GQNSEWOnly <- apply(resultsData, 1, regressionFunction)

GQNSEWOnlyDF <- bind_rows(GQNSEWOnly) %>% 
        mutate(estimate = ifelse(is.na(estimate), NA, ifelse(p.value <= 0.01, paste(round(estimate, 4), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 4), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 4), "*", sep=""), as.character(round(estimate, 4))))))) %>% 
        select(-p.value) %>% 
        spread(term, estimate) %>% 
        left_join(., yVars, by = c("yVar" = "varNames")) %>% 
        select(1, 7, 8, 5, 6, 3, 4, 2) %>% 
        arrange(yType, yVar)

names(GQNSEWOnlyDF)[6:7] <- c("GQ", "NSEW")

GQNSEWOnlyDF %>% 
        write_csv(., "../Results/Tables/GQNSEWOnly.csv")

```


```{r}
regressionFunctionAll <- function(x){
        depVar <- unlist(allData[x[1]], use.names = F)
        ##Select all the z variables
        capitalVar <- unlist(allData[x[2]], use.names = F)
        labourVar <- unlist(allData[x[3]], use.names = F)
        landVar <- unlist(allData[x[4]], use.names = F)
        productVar <- unlist(allData[x[5]], use.names = F)
        zVarCombo <- paste(x[1], x[2], x[3], x[4], sep = ",")
        
        modelZ <- plm(depVar ~ gqDistType + nsewDistType + capitalVar + labourVar+ landVar + productVar + gqDistType * postGQ + nsewDistType * postNSEW + gqDistType * postGQ * capitalVar + gqDistType * postGQ * labourVar + gqDistType * postGQ * landVar + gqDistType * postGQ * productVar + nsewDistType * postNSEW * capitalVar + nsewDistType * postNSEW * labourVar + nsewDistType * postNSEW * landVar + nsewDistType * postNSEW * productVar + spatialState * year, data = allData)
        
        interceptRow <- tibble(yVar = x[1], zVars = zVarCombo, term = "Intercept", estimate = mean(fixef(modelZ)), p.value = 0.0001)
        
        tidy(modelZ) %>% 
                filter(str_detect(term, "(?=.*DistType0-40)(?=.*post)")) %>% 
                mutate(zVars = zVarCombo, yVar = x[1]) %>% 
                select(yVar, zVars, term, estimate, p.value) %>% 
                bind_rows(., interceptRow)
}

allVars <- apply(resultsData, 1, regressionFunctionAll)

allVars <- bind_rows(allVars) %>% 
        mutate(estimate = ifelse(is.na(estimate), NA, ifelse(p.value <= 0.01, paste(round(estimate, 4), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 4), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 4), "*", sep=""), as.character(round(estimate, 4))))))) %>% 
        select(yVar, zVars, term, estimate) %>% 
        spread(term, estimate) %>% 
        separate(zVars, into = c("capitalVar", "labourVar", "landVar", "productVar"), sep = "\\,") %>% 
        left_join(., yVars, by = c("yVar" = "varNames")) %>% 
        select(1, 17, 18, 2:5, 11, 9, 15, 6, 12, 7, 13, 8, 14, 10, 16) %>% 
        arrange(yType, yVar)

namesComparison <- tibble(term = names(allVars))
names(allVars) <- c("yVar", "yType", "description","capitalVar", "labourVar", "landVar", "productVar", "Intercept", "GQ", "NSEW", "capitalGQ", "capitalNSEW", "labourGQ", "labourNSEW", "landGQ", "landNSEW", "productGQ", "productNSEW")
namesComparison$replacement <- names(allVars)
namesComparison

withZvars <- read_csv("../Results/Tables/GQNSEWMinimum1.csv")

identical(withZvars$capitalGQ, allVars$capitalGQ)
withZvars[withZvars$landGQ != allVars$landGQ, ]
```

##Misallocation regressions
```{r}
pattern <- "(?=.*DistType0-40)(?=.*post)"
regressionFunctionMis <- function(y){
        depVar <- unlist(allDataMis[y], use.names = F)

        modelZ <- plm(depVar ~ gqDistType + nsewDistType + mis_K_3b + mis_L_3b+ mis_T_3b + mis_Y_3b + gqDistType * postGQ + nsewDistType * postNSEW + gqDistType * postGQ * mis_K_3b + gqDistType * postGQ * mis_L_3b + gqDistType * postGQ * mis_T_3b + gqDistType * postGQ * mis_Y_3b + nsewDistType * postNSEW * mis_K_3b + nsewDistType * postNSEW * mis_L_3b + nsewDistType * postNSEW * mis_T_3b + nsewDistType * postNSEW * mis_Y_3b + spatialState * year, data = allDataMis)
        
        tidy(modelZ) %>% 
                filter(str_detect(term, pattern)) %>%
                        mutate(yVar = y, adjRSq = glance(modelZ)$adj.r.squared, nobs = nobs(modelZ)) %>%
                        select(yVar, term, estimate, p.value, adjRSq, nobs)
}

misResults <- lapply(yVars$varNames, regressionFunctionMis)

misResultsDF <- bind_rows(misResults) %>% 
        mutate(estimate = ifelse(is.na(estimate), NA, ifelse(p.value <= 0.01, paste(round(estimate, 4), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 4), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 4), "*", sep=""), as.character(round(estimate, 4))))))) %>% 
        select(yVar, term, estimate, adjRSq, nobs) %>% 
        spread(term, estimate) %>%
        left_join(., yVars, by = c("yVar" = "varNames"))%>% 
        arrange(yType, yVar) %>% 
        select(1, 14, 15, 2, 3, 8, 13, 4, 9, 5, 10, 6, 11, 7, 12)


names(misResultsDF)[6:15]<- c("GQ", "NSEW","misCapitalGQ", "misCapitalNSEW", "misLabourGQ", "misLabourNSEW", "misLandGQ", "misLandNSEW", "misOutputGQ", "misOutputNSEW")

write_csv(misResultsDF, "../Results/Tables/misAllocResults.csv")
```


##Continous treatment
```{r}
pattern <- "(?=.*Distance)(?=.*post)|(^postGQ$)|(^postNSEW$)"

allData <- allData %>%
        mutate(gqDistance = gqDistance/10, nsewDistance = nsewDistance/10)

continousRegressions <- function(y){
        depVar <- unlist(allData[y], use.names = F)
        
        model <- plm(depVar ~ gqDistance + nsewDistance + gqDistance * postGQ + nsewDistance * postNSEW, data = allData)
        
        tidy(model) %>% 
                filter(str_detect(term, pattern)) %>% 
                mutate(yVar = y, adjRSq = glance(model)$adj.r.squared, nobs = nobs(model)) %>% 
                select(yVar, term, estimate, p.value, adjRSq, nobs)
}

continousResults <- lapply(yVars$varNames, continousRegressions)

continousResultsDF <- bind_rows(continousResults) %>%
        mutate(estimate = ifelse(is.na(estimate), NA, ifelse(p.value <= 0.01, paste(round(estimate, 4), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 4), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 4), "*", sep=""), as.character(round(estimate, 4))))))) %>% 
        select(yVar, term, estimate, adjRSq, nobs) %>% 
        spread(term, estimate) %>%
        left_join(., yVars, by = c("yVar" = "varNames"))%>% 
        arrange(yType, yVar) %>% 
        select(1, 8, 9, 2, 3, 6, 7, 4, 5) %>% 
        write_csv(., "../Results/Tables/continousDistanceResults.csv")
        

```


##Base Regressions

```{r}
pattern <- "(?=.*DistType0-40)(?=.*post)|(^postGQ$)|(^postNSEW$)"

baseRegressions <- function(y){
        depVar <- unlist(allData[y], use.names = F)
        
        model <- plm(depVar ~ gqDistType + nsewDistType + gqDistType * postGQ + nsewDistType * postNSEW + spatialState * year, data = allData)
        
        tidy(model) %>% 
                filter(str_detect(term, pattern)) %>% 
                mutate(yVar = y, adjRSq = glance(model)$adj.r.squared, nobs = nobs(model)) %>% 
                select(yVar, term, estimate, p.value, adjRSq, nobs)
}

baseResults <- lapply(yVars$varNames,baseRegressions)

baseResultsDF <- bind_rows(baseResults) %>%
        mutate(estimate = ifelse(is.na(estimate), NA, ifelse(p.value <= 0.01, paste(round(estimate, 4), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 4), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 4), "*", sep=""), as.character(round(estimate, 4))))))) %>% 
        select(yVar, term, estimate, adjRSq, nobs) %>% 
        spread(term, estimate) %>%
        left_join(., yVars, by = c("yVar" = "varNames"))%>% 
        arrange(yType, yVar)%>% 
        select(1, 8, 9, 2, 3, 6, 7, 4, 5) %>% 
        write_csv(., "../Results/Tables/baseSpecFEApr25.csv")
        
```

