---
title: "Final Regression Sepcifications for the report"
output:
  html_notebook:
    number_sections: yes
  html_document: default
  pdf_document: default
date: '`r Sys.Date()`'
---
##Summary
Started this file on May 27th, 2017 to consolidate all the regressions for the final analysis. 

##Loading the data
First we load the following datasets.

1. The cleaned regression data
2. The outcome variables
3. The market variables
4. Regression formula for each outcome variable

```{r, message=FALSE}
rm(list = ls())
library(tidyverse); library(plm); library(broom); library(stringr); library(readxl)

##The regression data
load("../data/1 Cleaned files for analysis/allData.RDA")

##The list of variables
yVars <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/yVarsFinal.csv") %>% 
        select(varNames, yType, description) %>% 
        arrange(yType, varNames)

zVars <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/zVars.csv") %>% 
        arrange(zType, varNames)

##The regression formulas
regressionFormulaFinal <- read_csv("../data/1 Cleaned files for analysis/Regression Variables/finalSpecs.csv") %>% 
        mutate(spec = paste(yVar, terms, sep = " ~ "))
```

##Setting up for the regressions
This code chunk creates the names for the columns in the results tables.
```{r, message=FALSE}
namesList <- as.tibble(expand.grid(highway = c("GQ", "NSEW"), zVars = zVars$varNames)) %>% 
        mutate(termNames = paste(highway, zVars, sep = ":")) %>% 
        select(termNames)

namesList <- bind_rows(tibble(termNames = c("GQ", "NSEW")), namesList) %>% 
        arrange(termNames)
```

##Running the regressions
This section of the code loops through all the specs identified from the step wise process and extracts the terms we are interested in.

The final set of specs includes STATE * YEAR FE, I am dropping these for the current iteration.
```{r}
regressionFormulaFinal <- regressionFormulaFinal %>% 
        mutate(spec = str_replace(spec, "\\ spatialState \\*", "")) ## replace the state * year terms

```

Next, I add the terms with the governance index.

```{r}
regressionFormulaFinal <- regressionFormulaFinal %>% 
        mutate(spec = paste(spec, "+ gqDistType * postGQ * governanceIndex + nsewDistType * postNSEW * governanceIndex"))
```

We also need to add it to the names list for the final results.
```{r}
governanceNames <- paste(c("GQ:", "NSEW:"), "governanceIndex", sep = "")
namesList <- bind_rows(namesList, tibble(termNames = governanceNames)) %>% 
        arrange(termNames)
```


```{r, message=FALSE}
pattern <- "(?=.*DistType0-40)(?=.*post)" ##detect all double and triple interaction terms

runFinal <- function(y){
        yVar <- regressionFormulaFinal[regressionFormulaFinal$spec == y,]$yVar
        model <- plm(as.formula(y), data = allData)
        
        modelDF <- tidy(model) %>% 
                filter(str_detect(term, pattern)) %>%
                mutate(adjRSq = glance(model)$adj.r.squared, nobs = nobs(model)) %>%
                select(term, estimate, p.value, adjRSq, nobs) %>% 
                mutate(term = str_replace_all(term, c("gqDistType0-40:postGQ" = "GQ", "nsewDistType0-40:postNSEW" = "NSEW")))
        
        left_join(namesList, modelDF, by = c("termNames" = "term")) %>% ##join to the namesList
                mutate(yVar = yVar)
}

finalResults <- lapply(regressionFormulaFinal$spec, runFinal)
```



```{r}
finalResultsDF <- bind_rows(lapply(finalResults, bind_rows)) %>% 
        mutate(estimate = ifelse(is.na(estimate), NA, ifelse(p.value <= 0.01, paste(round(estimate, 4), "***", sep=""), ifelse(p.value <= 0.05, paste(round(estimate, 4), "**", sep=""), ifelse(p.value <= 0.1, paste(round(estimate, 4), "*", sep=""), as.character(round(estimate, 4))))))) 

finalResultsModelChars <- finalResultsDF %>% 
        select(yVar, nobs, adjRSq) %>% 
        group_by(yVar) %>% 
        summarise(nobs = unique(nobs[!is.na(nobs)]), adjRSq = unique(adjRSq[!is.na(adjRSq)])) %>% 
        ungroup()

finalResultsDF <- finalResultsDF %>% 
        select(yVar, term = termNames, estimate) %>% 
        spread(term, estimate) %>% 
        left_join(., finalResultsModelChars, by = "yVar") %>% 
        select(yVar, nobs, adjRSq, one_of(namesList$termNames)) %>% 
        left_join(., yVars, by = c("yVar" = "varNames")) %>% 
        select(1, 24, 25, 2:23) %>% 
        arrange(yType, yVar) %>% 
        mutate(adjRSq = round(adjRSq, 1)) %>%
        write_csv(., "../Results/Tables/resultsMay30thwithGovernanceIndex.csv")

```

